Democracy, Public Support, and Measurement Uncertainty

### 2021-06-20 paper/dcpo_demsupport.Rmd
use pure/exp_cls_ajps/apsr to execute moc.

```{r claassenMocUncertaintyAPSR}
load(here("data", "cls_apsr.rda"))

df_clsAPSR <- purrr::map(1:900, function(anEntry) {
  cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

@@

result_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_clsAPSR,aMod)
})

@@

saveRDS(result_clsUncertain, file = here("ouput","clsAPSR_uncertainty.RDS"))

@@

result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))

>>>>

```{r claassenMocUncertaintyAPSR}
load(here("data", "pure_cls_apsr.rda")) #use pure_cls_apsr instead of cls_apsr
load(here("data", "exp_cls_apsr.rda")) #use exp_cls_apsr instead of cls_apsr

df_clsAPSR <- purrr::map(1:900, function(anEntry) {
  pure_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

df_our_clsAPSR <- purrr::map(1:900, function(anEntry) {
  exp_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

@@

result_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_clsAPSR,aMod)
})  #claassen's data

result_our_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_our_clsAPSR,aMod)
})   ##our expanded data

@@

names(result_our_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_clsUncertain, file = here::here("ouput","clsAPSR_uncertainty.RDS"))

saveRDS(result_our_clsUncertain, file = here::here("ouput","our_clsAPSR_uncertainty.RDS"))

@@

#result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
result_clsUncertain <- readRDS(here("output","our_clsAPSR_uncertainty.RDS"))
result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))
